Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-26 volunteer-clouds-ieee-ci-si.tex
First abstract draft
Please @ccotap @mariosky @fergunet take a look at it, even if only to know the general paper layout. Remember that it's a special issue on metaheuristics software.

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Volunteer computing is used routinely in science and enterprise but it
still has a long way to go if it is going to become mainstream in the
same way the cloud in general has. The lack of general purpose tools
with analytics built in could be one of the reasons why this is so, as
well ad the lack of proofs of concept. That is why in this paper we
present NodIO, a client-server architecture for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser. The architecture, along with some initial results on the expected performance and scaling
behaviour is presented. We also use the algorithm analytics to try and
create a model of user behavior which, as is usual in this kind of
computing models, follow a Weibull distribution. 
\end{abstract}
